Nonlinear Tidal Dissipation in White Dwarfs

### 2018-01-20 proposal/NDSEG_personal.tex
proposals + check in review

\singlespacing

As an aspiring theoretical astrophysics professor, my goals consist of
developing both a strong grasp of pertinent numerical and analytical techniques
and a broad understanding of all science that can be observed in astrophysical
systems. Having this extra understanding will allow me to contribute to many
fields using the natural laboratories that astronomical objects supply, probing
physics inacessible to traditional experiment. To this end, the NDSEG fellowship
along with its associated benefits are a great fit for my goals, and I would
look forward to contributing to the NDSEG fellow community and the scientific
community at large.

My immediate priority in becoming a professor is to seek highly versatile,
interdisciplinary research to best prepare myself for future work. Such research
will build up a core skillset that can be applied to various fields. My proposed
research, numerical studies of nonlinear wave breaking in white dwarfs, is an
example of such research that combines high energy physics, fluid dynamics and
numerics. I intend to continue studying energetic phenomena in astrophysics...
% maybe one more goal

Ultimately, I seek to become a research professor developing simple, tractable
mobels of behaviors in astrophysical systems inacessible to man-made
laboratories. I believe such models are invaluable for turning astronomical
observations into constraints useful for other fields of study. My proposed work
accomplishes this by turning observed white dwarf luminosity and orbital
parameters into constraints on the behavior of matter under extreme conditions.
Furthermore, such models are

>>>>

\onehalfspacing

\textbf{Yubo Su Personal Statement}\\[\parskip]

As an aspiring theoretical astrophysics professor, my goals consist of
developing both a strong grasp of pertinent numerical and analytical techniques
and a broad understanding of all science that can be observed in astrophysical
systems. Having this extra understanding will allow me to contribute to various
fields using the natural laboratories that astronomical objects supply, probing
physics inacessible to traditional experiment. To this end, the NDSEG fellowship
along with its associated benefits are a great fit for my goals, and I would
look forward to contributing to the NDSEG community and the scientific community
at large.

My immediate priority in becoming a professor is to seek highly versatile,
interdisciplinary research to best prepare myself for future work. Such research
will build up a core skillset that can be applied to various fields. My proposed
research, numerical studies of nonlinear wave breaking in white dwarfs, is an
example of such research that combines high energy physics, fluid dynamics and
numerics. A second core component of building a transferrable skillset is
collaborating with scientists with diverse areas of expertise. The NDSEG
practicum will be a great opportunity both to meet research leaders in relevant
but different fields and to work alongside fellow growing scientists.

Ultimately, I seek to become a research professor developing simple, tractable
mobels of behaviors in astrophysical systems as probes of conditions
beyond man-made laboratories. I believe such models are invaluable for turning
astronomical observations into constraints useful for other fields of study. My
proposed work accomplishes this by turning observed white dwarf luminosity and
orbital parameters into constraints on the behavior of matter under extreme
conditions. My preference for simpler models is rooted in my excitement to
teach; intuitive models are more pedagogically suitable. Many of my best-taught
classes were transformative experiences for me, and I hope as part of my job to
instill the same clarity as did my professors.

My academic career to date has revolved around my goal of becoming an
interdisciplinary research and teaching faculty member developing simplified
models of intractable behavior. At Caltech, I pursued a double major and a
broad courseload that prepared me to apply many skills flexibly in my research.
I then worked for a year at a software startup, where I brought in many of my
problem solving skills from my physics background, and am now bringing industry
best practice to my research efforts at Cornell. I will therefore be well
prepared to bilaterally share knowledge between a DoD practicum and Cornell
research groups. Now, I have begun research with the versatile Professor Dong
Lai whose research centers on the same principle of distilling intractable
problems into intuitive, simplified models. My present track lines up well with
my desired goals, and I am primed to both contribute to and learn from an NDSEG
fellowship.
